Ear canal dynamic motion piezoelectric energy harvester using a bistable oscillator cycled by coupled hydraulic switches made of collapsed flexible tubes.

### 2022-09-30 article_system.tex
update

	%///////////////////////////////////////////// 
	\subsection{Targeted hydraulic behavior of the HVs}	
	\label{subsec:HV hydraulic targeted behavior}
	%/////////////////////////////////////////////
A multiphysic coupled model has been established with the equations and the preliminary dimensioning previously introduced. The unknown key aspect stays the hydraulic behavior $Cf(x_m)$ of the HVs. The numerical resolution of the differential equations can provide the necessary condition to satisfy in order to perform the adequate hydraulic commutation. In fact, the ratio between the pressure loss coefficient of the closed HV and the one of the opened HV has to be sufficient to force the flow through the opened branch. So we introduce $r_{Cf}$ as follows:
\begin{equation}
	r_{Cf} = \dfrac{Cf(\text{Closed HV})}{Cf(\text{Opened HV})}	= \dfrac{Cf_c}{Cf_0}	
	\label{eq:r_Cf_definition}
\end{equation}
Where $Cf_c=Cf(\pm x_0)$. The literature does not provide the constitutive relation between $x_m$ and $Cf$ for a buckled flexible tube. Therefore, we preliminarily assume that it is linear and defined as follows :
\begin{align}
	Cf(x_m) & = Cf_0 + \dfrac{Cf_c - Cf_0}{x_0}\ x_m  \notag \\
			& = Cf_0 \Biggl( 1 + \biggl(\dfrac{1}{r_{Cf}-1} \biggr)\dfrac{x_m}{x_0} \Biggr)
			\label{eq:Cf(x_m)_linear}
\end{align}
Regarding the BO symmetry, the relation between $Cf$ and $x_m$ has to be an even function to allow the system cycling, i.e. $Cf(x_m) = Cf(-x_m)$.

@@

The ratio $r_{Cf}$ has been increased until it was sufficient to prioritize the flow through the opened HV. The mastication cycle is identically quadrupled in order to test the system cycling robustness. Also, the earplug is assumed as a perfect flow rate source.

@@

The first phase consists on pushing on the BO mass to store potential energy, until the mass reaches $x=0$. During this phase, the fluid exciting the earplug is mostly guided toward the \emph{"bottom"} HC and the earplug pressure is generated by the BO counter-reaction force. The second phase begins after the mass crosses the $x_m=0$ position. The \emph{"top"} HV then opens ($Cf_{top} = Cf_0$) and the \emph{"bottom"} side HV closes ($Cf_{bot} = Cf(x_m)>Cf_0$). The fluid is then preferably guided toward the \emph{"top"} side and the contact between the mass and the HCs is non-existent. The mass goes oscillate around the opposite stable equilibrium position $x_0$ while a part on the oscillatory mechanical energy is converted in electricity by the APG. The cycling of the hydraulic branches is possible when $r_{Cf} =(r_{Cf})_{min}=26$.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[!htbp]
	\centering
	\captionsetup{justification=centering}
	\includegraphics[trim={0cm 0cm 0cm 0.5cm},clip, width=\textwidth]{figures/positions+DeltaV_debits_pear.pdf}
	\caption{}
	\label{fig:positions+DeltaV_debits_pear}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[!htbp]
	\centering
	\captionsetup{justification=centering}
	\includegraphics[trim={0cm 0cm 0cm 0.9cm},clip, width=\textwidth]{figures/positions_Up_puissances_energies.pdf}
	\caption{}
	\label{fig:positions_Up_puissances_energies}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\%
\section{EXPERIMENTAL CHARACTERIZATIONS}
\label{sec:EXPERIMENTAL CHARACTERIZATIONS}
%/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\%
    %///////////////////////////////////////////// 
	\subsection{The electromechanical converter}	
	\label{The electromechanical converter}
    %/////////////////////////////////////////////
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[!htbp]
\begin{center}
\captionsetup{justification=centering}
	\begin{subfigure} [h!]{0.49\textwidth}
		\includegraphics[trim={1.4cm 0cm 0cm 0cm},clip,width=\textwidth]{figures/monobloc+GPA_face.pdf}
		\caption{aaa} 
		\label{fig:/monobloc+GPA_face}
	\end{subfigure}
	%\hfill
	\begin{subfigure}[h!]{0.49\textwidth}
		\includegraphics[trim={6cm 3cm 7.5cm 2.6cm},clip, width=\textwidth]{figures/monobloc+GPA_iso.pdf}
		\caption{aaa}  
		\label{fig:/monobloc+GPA_iso}
	\end{subfigure}
	\caption{aaa}
\end{center}
\label{fig:/monobloc+GPA_face}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[!htbp]
	\centering
	\captionsetup{justification=centering}
	\includegraphics[trim={1cm 3cm 2cm 2.5cm},clip,width=0.45\textwidth]{figures/BDT_OB+GPA.pdf}
	\caption{Vue de face de GPA et l’OB monobloc sur le banc de caractérisation
	électromécanique.}
	\label{fig:BDT_OB+GPA}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%
\begin{table}[!htbp]
\centering
\captionsetup{justification=centering}
	\begin{tabular}{ c | c | c }
	\toprule
	& \textbf{Simulation with}  	   & \textbf{Simulation with}        \\
	& \textbf{theoretical}  		   & \textbf{recalibrated }			 \\
	\multirow{-3}{*}{\textbf{Symbol}}
	& \textbf{parameters}			   & \textbf{parameters} 			 \\
	\midrule
	$Q$                       & 50.0                  & 30.0 		  	\\  
	$f_0$                     & 47.0 Hz               & 27.9 Hz  		\\
	$x_0$                     & 0.49 mm               & 0.50 mm    		\\
	$K$                       & 2.56e5 N/m            & 0.85e5 N/m 		\\
	${k^2_{sys}}$             & 8.72 \%               & 1.25 \% 		\\
	$\eta_{bo}$               & 79 \%                 & 12.9 \%   		\\
	\bottomrule
	\end{tabular}
	\caption{Theoretical and experimentally recalibrated values of the electromechanical converter.}
	\label{tab:parametres_lacher_free}
\end{table} 
%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[!htbp]
	\centering
	% \resizebox{\textwidth}{!}{%
		\begin{tabular}[t]{c|c|c}
\toprule
\multicolumn{1}{c}{\textbf{Paramètre}}	&
\multicolumn{1}{c}{\textbf{Valeur OB}} 	& 
\multicolumn{1}{c}{\textbf{Valeur OBVH}}  \\
\midrule
$D_g$ [mm] 						& \cellcolor{ashgrey} 		& \textcolor{red}{4} 		\\ \hline
$\Delta\theta$ [deg] 			& \cellcolor{ashgrey} 		& \textcolor{red}{{[$\approx$ 19 ; $\approx$ 36]}} \\ \hline
$K_{T100p}(\theta_f)$ [Nmm/rad] & \cellcolor{ashgrey}  		&  0.27 					\\ \hline
$a$ [mm]         			    & \cellcolor{ashgrey}  		&  2.24				 	 	\\ \hline
$\mu_{fs}$ [~~] 				& \cellcolor{ashgrey}  		&  0.42  					\\ \hline
$K$ [N/m] 						&	84480			  	 	&  84480  					\\ \hline
$x_0$ [mm] 						& \textcolor{red}{0.59}		& \textcolor{red}{0.50}  	\\ \hline
$v_0$ [mm/s] 					& \textcolor{red}{10}		& \textcolor{red}{65}  		\\ \hline
$Q$	[~~] 						& 		24.0		 		& 5.0     					\\ \hline
$k^2_{sys}$ [\%] 				& 		1.25		 		& \textcolor{red}{1.25}   	\\ \hline
$\eta_{ob}$ [\%] 				& 		11.9		 		& 2.6   					\\ \hline	
$R_{ch}$ [k$\text{\ohm}$] 		&	\textcolor{red}{15.5}	& \textcolor{red}{15.5}    	\\ \hline		
$m$	[g]						    &	\textcolor{red}{5.88}	& 9.00   					\\ \hline	
$f_0$ [Hz]						&		32.9				& 27.9   					\\
\bottomrule	
	\end{tabular}
        \caption{Valeur des paramètres de l'OB et de l'ensemble OBVH implémentant le tube T100p suite au essais de lâchers expérimentaux}
        \label{tab:parametres lacher tube}
\end{table}        
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

	%///////////////////////////////////////////// 
	\subsection{Targeted hydraulic behavior of the HVs}	
	\label{subsec:HV hydraulic targeted behavior}
	%/////////////////////////////////////////////
A multiphysic coupled model has been established with the equations and the preliminary dimensioning previously introduced. The unknown key aspect stays the hydraulic behavior $Cf(x_m)$ of the HVs. The numerical resolution of the differential equations can provide the necessary condition to satisfy in order to perform the adequate hydraulic commutation. In fact, the ratio between the pressure loss coefficient of the closed HV and the one of the opened HV has to be sufficient to force the flow through the opened branch. So we introduce the hydraulic restriction coefficient $r_{Cf}$ defined as follows :
\begin{equation}
	r_{Cf} = \dfrac{Cf(\text{Closed HV})}{Cf(\text{Opened HV})}	= \dfrac{Cf_c}{Cf_0}	
	\label{eq:r_Cf_definition}
\end{equation}
Where $Cf_c=Cf(\pm x_0)$. The literature does not provide the constitutive relation between $x_m$ and $Cf$ for a buckled flexible tube. Therefore, we preliminarily assume that it is linear and defined as follows :
\begin{align}
	Cf(x_m) & = Cf_0 + \dfrac{Cf_c - Cf_0}{x_0}\ x_m  \notag \\
			& = Cf_0 \Biggl( 1 + \biggl(\dfrac{1}{r_{Cf}-1} \biggr)\dfrac{x_m}{x_0} \Biggr)
			\label{eq:Cf(x_m)_linear}
\end{align}
Regarding the BO symmetry, the relation between $Cf$ and $x_m$ has to be an even function to allow the system cycling, i.e. $Cf(x_m) = Cf(-x_m)$.

@@

The ratio $r_{Cf}$ has been increased until it was sufficient to prioritize the flow through the opened HV. The mastication cycle is identically quadrupled in order to test the system cycling robustness. Also, the earplug is assumed as a perfect flow rate source. The calculated and the resulting theoretical parameters of the simulated global model are presented in tables \ref{tab:parametres électromécaniques} and \ref{tab:parametres_hydrauliques}.

@@

The first phase consists on pushing on the BO mass to store potential energy, until the mass reaches $x=0$. During this phase, the fluid exciting the earplug is mostly guided toward the \emph{"bottom"} HC and the earplug pressure is generated by the BO counter-reaction force. The second phase begins after the mass crosses the $x_m=0$ position. The \emph{"top"} HV then opens ($Cf_{top} = Cf_0$) and the \emph{"bottom"} side HV closes ($Cf_{bot} = Cf(x_m)>Cf_0$). The fluid is then preferably guided toward the \emph{"top"} side and the contact between the mass and the HCs is non-existent. The mass goes oscillate around the opposite stable equilibrium position $x_0$ while a part on the oscillatory mechanical energy is converted in electricity by the APG. The flow rate goes toward the right piston when $r_{Cf}$ is set at a minimum value of \mbox{$(r_{Cf})_{min}=26$}.

Figure \ref{fig:positions_Up_puissances_energies} additionally presents the different positions of the moving components, the APG voltage, the source and harvested powers and the different energies entering and exciting the system. The theoretical global efficiency of the harvester is evaluated at $\eta_g=67.1$\% with 20µJ harvested from one mastication. The energy losses are mostly located in the BO stage and depend on the quality factor $Q$ that has been set in accordance with previous work results on similar BO architectures \cite{Liu2013}. The energy source depends on the comfort pressure level $p_c$ that is set to 1kPa here, i.e. a fraction of the theoretical maximal value of $12$kPa \cite{Bouchard-Roy2020}. The harvester efficiency could lead to a theoretical maximum of $342$µJ extractable from the ear canal.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[!htbp]
	\centering
	\captionsetup{justification=centering}
	\includegraphics[trim={0cm 0cm 0cm 0.5cm},clip, width=\textwidth]{figures/positions+DeltaV_debits_pear.pdf}
	\caption{}
	\label{fig:positions+DeltaV_debits_pear}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[!htbp]
	\centering
	\captionsetup{justification=centering}
	\includegraphics[trim={0cm 0cm 0cm 0.9cm},clip, width=\textwidth]{figures/positions_Up_puissances_energies.pdf}
	\caption{}
	\label{fig:positions_Up_puissances_energies}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%	
\begin{table}	
	\centering
	\begin{tabular}{c|c|c}
\toprule
\multicolumn{1}{c}{~~\textbf{Parameter}~~}  & \multicolumn{1}{c}{~~\textbf{Value}~~} & \multicolumn{1}{c}{~~\textbf{[Unit]}~~}  \\
\midrule
$K$					&	0.256			& [$N/\mu m$]			\\ \hline
$x_0$				&	0.49			& [$mm$] 				\\ \hline
$L$					&	16.0			& [$mm$] 				\\ \hline
$m$					&	5.88			& [$g$] 				\\ \hline
$x_{c0}$			&	0.69			& [$mm$] 				\\ \hline
$R_{ch}$			&	15.5			& [$k\Omega$] 			\\ \hline
$\alpha$			&   0.105			& [$N/V$] 				\\ \hline
$C_0$	   			&	0.25			& [$\mu F$]				\\ \hline
$Q$ 				&	50				& [-] 					\\ \hline
$\eta_g$			& 	67.1			& [$\%$]		\\ 
\bottomrule
	\end{tabular}
	\caption{Electromechanical parameters}
	\label{tab:parametres électromécaniques}
\end{table}
\begin{table}
	\centering
	\begin{tabular}{c|c|c}
\toprule
\multicolumn{1}{c}{~~\textbf{Parameter}~~}  & \multicolumn{1}{c}{~~\textbf{Value}~~} & \multicolumn{1}{c}{~~\textbf{[Unit]}~~}  \\
\midrule
$D_{hc}$  	   				&	4				& [$mm$]			\\ \hline
$a_h$					&	7.2				& [-]				\\ \hline
$p_c$					&	1				& [$kPa$]			\\ \hline
$\Delta V{ear,m}$		& 60				& [$mm^3$]			\\ \hline
$Cf_0$					&	0.21e17			&[$Pa.s^2m^{-6}$]	\\ \hline
$Cf_c$					&	5.46e17			&[$Pa.s^2m^{-6}$]	\\
\bottomrule 
	\end{tabular}
	\caption{Hydraulic parameters}
	\label{tab:parametres_hydrauliques}
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The simulated model shows promising efficiency and demonstrates that a minimum value of 26 is required on the hydraulic restriction coefficient $r_{Cf}$ to ensure the adequate cycled actuation of the BO mass. Next section will present the experimental approach to validate the theoretical behavior of the electromechanical converter.

%/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\%
\section{EXPERIMENTAL CHARACTERIZATION OF THE \mbox{ELECTROMECHANICAL} CONVERTER}
\label{sec:EXPERIMENTAL CHARACTERIZATIONS OF THE ELECTROMECHANICAL CONVERTER}
%/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\%
    %///////////////////////////////////////////// 
	\subsection{The electromechanical converter presentation}	
	\label{The electromechanical converter presentation}
    %/////////////////////////////////////////////
The device heart is the electromechanical converter composed of the BO implementing the APG and therefore, they have been designed with respect to space requirements. We opted for a monobloc structure with blades in order to optimize the oscillator quality factor by avoiding screw assemblies. Figure \ref{fig:monobloc_face} shows the face view of the monobloc bistable oscillator CAD that has been fabricated by electrical discharge machining (EDM). The 8 hinges are assured by 4 buckled blades (BB) and a vertical guide blade (GB) ensures the APG mounting. The efficient part composed of the blades and the central mass are $1.2$mm think. The external rigid 6mm thick frame has been designed to ensure the fixed boundary conditions and also to allow the mounting of both the measurement instruments and the HCs. The geometrical and mechanical parameters of the BO are referenced in table \ref{tab:parametres_lames}. The following sections describe the design method that led to the values of the different parameters, depending on our needs.
%%%%%%%%%%%%%%%%%
\begin{table}[!htbp]
	\centering
    \resizebox{\linewidth}{!}{%
		\begin{tabular}{l|c|c}
			\toprule
\textbf{Parameter definition} & \textbf{Symbol}    & \textbf{Valeur [Unit]} \\
\midrule
APX4 steel Young's modulus     & $E$                       & 211 [GPa]  \\
APX4 steel elastic resistance  & $Re_{APX4}$               & 955[MPa]    \\
Dimensions of a buckled blade  & $L$ x $l$ x $e$           & 16x0.07x1.2 [mm] \\
Dimensions of the guide blade  & $L_{v}$ x $l_{v}$ x $e$   & 17.5x0.07x1.2 [mm] \\
% Mounted GB dimensions          & $L_{v2}$ x $l_{v2}$ x $e$ & 48x0.1x1.2 [mm] \\
Soft hinge stiffness		   & $K_{\varphi}$             & 0.006 [Nm/rad] \\
Stiffness of the guide blade along $\vec{z}$  & $K_{gb}$   & 190 [N/m] \\
Stiffness of 4 buckled blades along $\vec{z}$ & $K_{bb}$   & 1402 [kN/m] \\  
Stiffness of the APG along $\vec{z}$          & $K$        & 252  [kN/m]\\
			\bottomrule
		\end{tabular}}
	\caption{Definitions and values of the fabricated BO}
	\label{tab:parametres_lames}
\end{table}
%%%%%%%%%%%%%%%%%%%%% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[!htbp]
\centering
\captionsetup{justification=centering}
	\includegraphics[trim={19.2cm 0cm 0cm 5cm},clip,width=.7\linewidth]{figures/monobloc_face.pdf}
	\caption{Face transparency view of the monobloc BO CAO}
\label{fig:monobloc_face}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    %///////////////////////////////////////////// 
	\subsection{The electromechanical converter presentation}	
	\label{The electromechanical converter presentation}
    %/////////////////////////////////////////////

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[!htbp]
	\centering
	\captionsetup{justification=centering}
	\includegraphics[trim={1cm 3cm 2cm 2.5cm},clip,width=0.45\textwidth]{figures/BDT_OB+GPA.pdf}
	\caption{Vue de face de GPA et l’OB monobloc sur le banc de caractérisation
	électromécanique.}
	\label{fig:BDT_OB+GPA}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%
\begin{table}[!htbp]
\centering
\captionsetup{justification=centering}
	\begin{tabular}{ c | c | c }
	\toprule
	& \textbf{Simulation with}  	   & \textbf{Simulation with}        \\
	& \textbf{theoretical}  		   & \textbf{recalibrated }			 \\
	\multirow{-3}{*}{\textbf{Symbol}}
	& \textbf{parameters}			   & \textbf{parameters} 			 \\
	\midrule
	$Q$                       & 50.0                  & 30.0 		  	\\  
	$f_0$                     & 47.0 Hz               & 27.9 Hz  		\\
	$x_0$                     & 0.49 mm               & 0.50 mm    		\\
	$K$                       & 2.56e5 N/m            & 0.85e5 N/m 		\\
	${k^2_{sys}}$             & 8.72 \%               & 1.25 \% 		\\
	$\eta_{bo}$               & 79 \%                 & 12.9 \%   		\\
	\bottomrule
	\end{tabular}
	\caption{Theoretical and experimentally recalibrated values of the electromechanical converter.}
	\label{tab:parametres_lacher_free}
\end{table} 
%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[!htbp]
	\centering
	% \resizebox{\textwidth}{!}{%
		\begin{tabular}[t]{c|c|c}
\toprule
\multicolumn{1}{c}{\textbf{Parameter}}	&
\multicolumn{1}{c}{\textbf{Value OB}} 	& 
\multicolumn{1}{c}{\textbf{Value OBVH}}  \\
\midrule
$D_g$ [mm] 						& \cellcolor{ashgrey} 		& \textcolor{red}{4} 		\\ \hline
$\Delta\theta$ [deg] 			& \cellcolor{ashgrey} 		& \textcolor{red}{{[$\approx$ 19 ; $\approx$ 36]}} \\ \hline
$K_{T100p}(\theta_f)$ [Nmm/rad] & \cellcolor{ashgrey}  		&  0.27 					\\ \hline
$a$ [mm]         			    & \cellcolor{ashgrey}  		&  2.24				 	 	\\ \hline
$\mu_{fs}$ [~~] 				& \cellcolor{ashgrey}  		&  0.42  					\\ \hline
$K$ [N/m] 						&	84480			  	 	&  84480  					\\ \hline
$x_0$ [mm] 						& \textcolor{red}{0.59}		& \textcolor{red}{0.50}  	\\ \hline
$v_0$ [mm/s] 					& \textcolor{red}{10}		& \textcolor{red}{65}  		\\ \hline
$Q$	[~~] 						& 		24.0		 		& 5.0     					\\ \hline
$k^2_{sys}$ [\%] 				& 		1.25		 		& \textcolor{red}{1.25}   	\\ \hline
$\eta_{ob}$ [\%] 				& 		11.9		 		& 2.6   					\\ \hline	
$R_{ch}$ [k$\text{\ohm}$] 		&	\textcolor{red}{15.5}	& \textcolor{red}{15.5}    	\\ \hline		
$m$	[g]						    &	\textcolor{red}{5.88}	& 9.00   					\\ \hline	
$f_0$ [Hz]						&		32.9				& 27.9   					\\
\bottomrule	
	\end{tabular}
        \caption{Value des paramètres de l'OB et de l'ensemble OBVH implémentant le tube T100p suite au essais de lâchers expérimentaux}
        \label{tab:parametres lacher tube}
\end{table}        
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
